### 2024-05-31 texts/paper_closing.tex
minor lit review and text updates (latex export)

% Created 2024-05-03 vr 10:56
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\setlength{\parindent}{1.2cm}
\author{Johannes }
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Johannes },
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.2 (Org mode 9.6.26)}, 
 pdflang={English}}
\begin{document}

@@

\subsection*{private museum 3 crisis}

@@

\subsection*{Private museums}

Investigating the survival prospects of private museum furthermore illucidates the long-term development of the organizational form as a whole.
While the composition of private museums is not only influenced by closures, but also by foundings, analysing the former provides insights in the sustainability of

Given the non-significant gender difference, it can be expected that (unless given a strong increase in founding by women) the population of private museums will continue to remain a dominated affair\footnote{The point estimates, which are higher for women and couples, albeit not significantly so, even point towards a slight expansion of the proportion of museums established by men.}
The role of the founder is two sided.
Death and exclusion from a prestigious ranking are not associated with a higher risk of closure, which indicates that private museums have attained a substantial degree of institutionalization.
On the other hand, self-identifying as an institution which is not a museum, foundation or collection possibly reflects a kind of founder attitudes which substantially influences survival chances.
Founders who are less interested in establish institutions might be more inclined to choose a name which less reflects this ambition. 
One way of conceptualizing this distinction might then be that whereas involuntary, externally imposed events are less able to close museums of otherwise motivated founders, some founders might from the very beginning voluntarily decide to not establish a museum that is intended for perpetuity.

However, this group is somewhat small.
Of the XXX museums included in the database, XXX do not carry the term museum, foundation or collection.
Thus given this low share, and the corresponding  higher closing rate, a possible future for the private museum population might be increased institutionalization and consolidation of relatively robust organizations.
The effects of location might be seen
On the one hand, museum location is chosen by the founder at the time of founding (or rather, several years in advance).
This gives founders substantial choice in the size and composition of the potential audience who will be able to easily assess the museum.
On the other hand, collectors are less able to influence what plans other collectors might have.
What may have been at one point been identified as a promising location without substantial competition may turn out to be a much less fertile ground as soon as other collectors start eyeing the same region for their own private museum projects.
In particular private museum in rural locations with low population densities seem to be at risk when other museums open in the neighborhood. 
This is not to say that private museums cannot endure in areas with low population densities. 
In fact, at low numbers of private museums in the neighborhood their survival prospects are better than those located in larger cities.
These larger cities with low private museum counts are possibly also characterized by lower numbers of other cultural institutions as well as an audience less interested in postmaterial art consumption.

@@

As a substantial literature on organizational survival exists,

@@

An identity that is legitimate (understandable) and favorable (positive) has been shown to have a vast number of positive outcomes for organizations \parencite{Lange_Lee_Dai_2010_reputation}.
As gaining the approval of different stakeholders is necessary for being understood and/or supported by other organizations in the environment, having a clearly defined and favorable identity influences resource acquisition and thereby survival prospects \parencite{Rao_1994_reputation}.
Even for non-profit organizations such as museums, which do not produce tangible goods (a domain where identity-related effects are present, e.g. \cite{Hsu_2015_granted,Bogaert_etal_2014_ecological}), a clear and positive identity might be helpful in a number of ways:
In particular in the context of private museums, decline of legitimacy or reputation could lead to lower visitor numbers, less discounts from art dealers, less government grants or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.

@@

Furthermore, identity of a private museum may be influenced by the identity of persons most closely affiliated with it, in particular the identity of its founders.
Given that founders are the very reason behind the existence of these organizations, and sometimes plan these as their personal legacies \parencite{Walker_2019_collector}, founder status gains or losses may very well reflect on the wider organization and affect its survival propspects.

@@

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri May  3 10:55:27 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrll}
  \hline 
 \multicolumn{1}{l}{Self-identification} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Self-ID (recoded)} & \multicolumn{1}{l}{examples}\\ 
 \hline
 Museum & 190 & Museum & Museum Kampa, Museum Barberini \\ 
  Foundation & 104 & Foundation & Marciano Art Foundation, Hill Art Foundation \\ 
  Collection &  69 & Collection & The Farjam Collection, Sammlung Boros \\ 
  None &  64 & Other & The Bunker, The Broad \\ 
  Center &  17 & Other & Dairy Art Centre, Art Center Nabi \\ 
  Gallery &  14 & Other & Saatchi Gallery, Galerie C15 \\ 
  Art space &  13 & Other & El Espacio 23, Qiao Space \\ 
  House / villa &  11 & Other & Villa La Fleur, Casa Daros Rio \\ 
  Institute &  10 & Other & Instituto Inhotim, Woods Art Institute \\ 
  Kunsthalle &   8 & Other & Kunsthalle Würth, G2 Kunsthalle \\ 
  Park / garden &   3 & Other & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
   \hline
\end{tabular}
\caption{Selfidentification} 
\label{tbl:t_selfid}
\end{table}

Two measures are constructed that aim to capture an effect of legitimacy on closing.
First, self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent, see table \ref{tbl:t_selfid}).
Since the name is one of the first aspects that stakeholders perceive when engaging with an organization, it might very well shape expectations and influence forms of engagement.
In particular, it might be that museums that also refer to themselves as museums are seen as more favorable and worthy of visits, collaborations and support than other museums.

Secondly, a binary predictor measures whether the museum is included in the "Museums of the World" (MOW) database \parencite{deGruyter_2021_MOW}, a database containing over 55.000 museums.
While the exact criteria of the research process leading to the MOW database are not known, it is plausible that museums who correspond to an ideal-typical museum are more likely to be included.
Assuming that museums are seen similarly by the creators of the MOW database and other audiences, inclusion in the MOW database constitutes a proxy for adherence to museum standards.

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri May  3 10:55:26 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 294 & 0.584 & 6.0e-01 &   0.49 & 0 & 1 \\ 
   & Gender - Female & 79 & 0.157 & 1.7e-01 &   0.37 & 0 & 1 \\ 
   & Gender - Couple & 130 & 0.258 & 2.3e-01 &   0.42 & 0 & 1 \\ 
   & Founder - alive & 440 & 0.875 & 9.0e-01 &   0.30 & 0 & 1 \\ 
   & Founder - died recently & 17 & 0.034 & 1.9e-02 &   0.13 & 0 & 1 \\ 
   & Founder - died 2+ years ago & 46 & 0.091 & 7.9e-02 &   0.27 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 190 & 0.378 & 4.1e-01 &   0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 104 & 0.207 & 1.9e-01 &   0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 69 & 0.137 & 1.3e-01 &   0.34 & 0 & 1 \\ 
   & Self-Identification - Other & 140 & 0.278 & 2.7e-01 &   0.45 & 0 & 1 \\ 
   & Founder name in Museum name & 240 & 0.477 & 4.8e-01 &   0.50 & 0 & 1 \\ 
   & MOW inclusion & 92 & 0.183 & 2.7e-01 &   0.45 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  & 8.0e-01 &   0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  & 1.4e-01 &   0.35 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  & 5.3e-02 &   0.23 & 0 & 1 \\ 
   & Exhibition any &  &  & 6.3e-01 &   0.48 & 0 & 1 \\ 
   & Exhibition any last 5 years &  &  & 4.6e-01 &   0.50 & 0 & 1 \\ 
   & PC1 (Size) & 112.930441195886 & 0.225 & 1.8e-01 &   1.90 & -6.5 & 2.61 \\ 
   & PC2 (Support) & 90.555299883145 & 0.180 & 2.0e-01 &   1.52 & -5.1 & 2.71 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  & 4.5e-01 &   1.26 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  & 1.3e+00 &   1.68 & 0.000087 & 10.81 \\ 
   & Pop. (millions) country &  &  & 1.6e+02 & 292.68 & 0.037 & 1412.36 \\ 
   & Nbr PM within 10km &  &  & 1.8e+00 &   3.14 & 0 & 16 \\ 
   & PM density (10km) &  &  & 1.7e+00 &   4.93 & 0 & 76.37 \\ 
   & Europe and North America & 320 & 0.636 & 6.4e-01 &   0.48 & 0 & 1 \\ 
   & Region - Africa & 8 & 0.016 & 1.2e-02 &   0.11 & 0 & 1 \\ 
   & Region - Asia & 142 & 0.282 & 2.9e-01 &   0.45 & 0 & 1 \\ 
   & Region - Europe & 248 & 0.493 & 5.0e-01 &   0.50 & 0 & 1 \\ 
   & Region - Latin America & 23 & 0.046 & 4.2e-02 &   0.20 & 0 & 1 \\ 
   & Region - North America & 72 & 0.143 & 1.4e-01 &   0.34 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.020 & 1.9e-02 &   0.13 & 0 & 1 \\ 
   & year &  &  & 2.0e+03 &   5.72 & 2000 & 2021 \\ 
   & Time Period 2000-2004 &  &  & 1.0e-01 &   0.30 & 0 & 1 \\ 
   & Time Period 2005-2009 &  &  & 1.7e-01 &   0.37 & 0 & 1 \\ 
   & Time Period 2010-2014 &  &  & 2.6e-01 &   0.44 & 0 & 1 \\ 
   & Time Period 2015-2019 &  &  & 3.3e-01 &   0.47 & 0 & 1 \\ 
   & Time Period 2020-2024 &  &  & 1.4e-01 &   0.35 & 0 & 1 \\ 
   & Great Recession (2008/09) &  &  & 7.6e-02 &   0.27 & 0 & 1 \\ 
   & Covid Pandemic (2020/21) &  &  & 1.4e-01 &   0.35 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

Overall the entire life span, the average hazard rate is 0.87\%, which allows comparison to other studies of NPO closure.
While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})

@@

Comparison to other forms of nonprofit organizations reported by \parencite{Gordon_etal_2013_insolvency}
places private museum at a risk similar to that of animal shelters and zoos (0.7\%), botanical \& environmental centers (0.8\%), colleges and universities (0.8\%), food and agricultural-oriented human service organizations (0.8\%) and  student and educational services (0.8\%).
While the diversity of non-profit organizations makes comparisons to its entirety difficult, it is still worthwhile to consider that the average hazard of private museums 0.87\% is around half that of that NPOs generally (1.58\%, see table \ref{tbl:litreview2} for studies on wider nonprofit populations).
It is furthermore substantially lower than that of youth centers (1.4\%), children-focused human services (2.4\%), K12 schools (1.8\%), mental health organizations (2.4\%) or performing arts organizations (3.7\%).
In fact, lower dissolution rates are only reported for historical societies (0.5\%) and libraries (0.2\%).

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri May  3 10:55:34 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .02 \; (0.34) \\ 
   & Gender - Couple & -.10 \; (0.32) \\ 
   & Founder - died recently & 1.09 \; (0.61) \\ 
   & Founder - died 2+ years ago & -.06 \; (0.55) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .25 \; (0.42) \\ 
   & Self-Identification - Collection & -.46 \; (0.54) \\ 
   & Self-Identification - Other & 1.12 \; (0.31)^{***} \\ 
   & AN Ranking - Included & .25 \; (0.35) \\ 
   & AN Ranking - Dropped & .51 \; (0.50) \\ 
   & Founder name in Museum name & .09 \; (0.28) \\ 
   & Exhibition any & -.22 \; (0.27) \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .63 \; (0.35) \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} \\ 
   & Great Recession (2008/09) & -1.61 \; (1.01) \\ 
   & Covid Pandemic (2020/21) & .39 \; (0.29) \\ 
   \hline
 & Museum-years & 6096 \\ 
   & Closures & 68 \\ 
   & log. Likelihood & -338.36 \\ 
   & AIC & 712.73 \\ 
   & BIC & 752.68 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

@@

@@

For this study, I only investigated the occurence of closure events.
However, private museums can stop existing as private museums not just by closing down, but also by being transformed into other organizational forms.
One way in which this can happen is when other parties, such as local governments other philanthropists, foundations, or corporations become substantially involved in the ownership, governance and/or funding of the museum.
Sometimes this involves changes in the composition of the board of directors, with new parties gaining seats and hence influence in decision-making, thereby diminishing the private character of the museum, often to an extent that it no longer fits the working definition.
Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was often not feasible to determine the date of such transitions\footnote{As a consequence of this, they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing. However, as their numbers are limited to 25 entries in the database, the bias this introduces into closing risks is likely not substantial.}
Primarily this was due to the intransparency of these organizations, as well as the gradual process.
As the presence of non-founder members does not categorically exclude a museum from being categorized as private museum as long as third-party influence is limited, this influence can grow until the museum bears little resemblance to its former self.
The possibility of other outcomes than surival and closures has been investigated for NPOs more generally
\parencite{Searing_2020_zombies,HernandezOrtiz_2022_discontinuity,Helmig_Ingerfurth_Pinz_2013_nonprofit}, and for private museums specifically: 
\textcite{Walker_2019_collector} argues that in the case of Germany, private museum founders turn to the state to ensure the survival of their projects in the form of public-private partnerships.
Investigating this process of transformation into a different organizational form thus provides fruitful avenue for further research.

environment can be measured more
\begin{itemize}
\item geocoding of other institutiosn
\item tax incentives
\item government spending
\end{itemize}
-> this might futher specify the niches in which PMs can endure
\end{document}

>>>>

% Created 2024-05-30 do 10:16
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\setlength{\parindent}{1.2cm}
\author{Johannes }
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Johannes },
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.3 (Org mode 9.6.26)}, 
 pdflang={English}}
\begin{document}

@@

\subsection*{lack of regulation -> museums are relatively free as long as they have money}

Museums are subject to relatively little regulation (the term "museum" is not a legally protected term and can be generally used without certification \parencite{Museumsbund_ICOMDE_2006_standards,Moore_2022_best,Lister_2023_marketing}.
Museum associations on the national (e.g. American Alliance of Museums (AAM) for the United States, Museumsbund for Germany) or international (International council of museums, ICOM) level exist, which aim to standardize e.g. museum setup and operations, such as in relations to ethics \parencite{ICOM_2016_ethics} or sustainability \parencite{Bickersteth_2016_environment}. 
Membership for institutions is voluntary, and in practice limited:
ICOM has around 3,000 institutional members \parencite{ICOM_2020_report19}, a relatively small fraction of the over 104,000 museums estimated to exist globally \parencite{UNESCO_2021_covid}. \footnote{The absence of clear criteria what constitutes a museum prevents standardized data collection which would be necessary to generate exact numbers.}
National associations fare somewhat better, with e.g. the AAM representing over 4,000 of the country's 35,000 museums \parencite{LOC_2019_AAM}, and the German Museumsbund representing over 1,300 \parencite{Museumsbund_2024_mitgliedmuseen} of Germany's 7,120 museums \parencite{IMF_2024_museumsstatistik}.
Even among its members promoting standards appears difficult, as shown in the establishment of the museum definition:
After an ICOM proposal was rejected in 2019 after heated debates, an 18-month, four-round deliberation process involving 126 national committees was required to agree on a new definition by 2022 \parencite{Robinson_2021_debating,Seymour_2022_definition}.

@@

@@

As a substantial literature on organizational survival exists, thus

@@

An identity that is legitimate (understandable) and favorable (positive) has been argued to have a vast number of positive outcomes for organizations \parencite{Lange_Lee_Dai_2010_reputation}.
As gaining the approval of different stakeholders is necessary for being understood and/or supported by other organizations in the environment, having a clearly defined and favorable identity influences resource acquisition and thereby survival prospects \parencite{Rao_1994_reputation}.
Even for non-profit organizations such as museums, which do not produce tangible goods (a domain where identity-related effects are present, e.g. \cite{Hsu_2015_granted,Bogaert_etal_2014_ecological}), a clear and positive identity might be helpful in a number of ways:
In particular in the context of private museums, decline of legitimacy or reputation could lead to lower visitor numbers, less discounts from art dealers, less government grants or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.

@@

Furthermore, identity of a private museum may be influenced by the identity of persons most closely affiliated with it, in particular the identity of its founders.
Given that founders are the very reason behind the existence of these organizations, and sometimes plan these as their personal legacies \parencite{Walker_2019_collector}, founder status gains or losses may reflect on the wider organization and affect its survival propspects.

@@

\subsubsection*{Shocks}

External shocks can

\subsubsection*{Size}

Where

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon May 27 11:25:43 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrll}
  \hline 
 \multicolumn{1}{l}{Self-identification} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Self-ID (recoded)} & \multicolumn{1}{l}{examples}\\ 
 \hline
 Museum & 190 & Museum & Museum Kampa, Museum Barberini \\ 
  Foundation & 104 & Foundation & Marciano Art Foundation, Hill Art Foundation \\ 
  Collection &  69 & Collection & The Farjam Collection, Sammlung Boros \\ 
  None &  64 & Other & The Bunker, The Broad \\ 
  Center &  17 & Other & Dairy Art Centre, Art Center Nabi \\ 
  Gallery &  14 & Other & Saatchi Gallery, Galerie C15 \\ 
  Art space &  13 & Other & El Espacio 23, Qiao Space \\ 
  House / villa &  11 & Other & Villa La Fleur, Casa Daros Rio \\ 
  Institute &  10 & Other & Instituto Inhotim, Woods Art Institute \\ 
  Kunsthalle &   8 & Other & Kunsthalle Würth, G2 Kunsthalle \\ 
  Park / garden &   3 & Other & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
   \hline
\end{tabular}
\caption{Selfidentification} 
\label{tbl:t_selfid}
\end{table}

Two measures are constructed that aim to capture an effect of legitimacy on closing.
First, self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent, see table \ref{tbl:t_selfid}).
Since the name is one of the first aspects that stakeholders perceive when engaging with an organization, it might shape expectations and influence forms of engagement.
In particular, it might be that museums that also refer to themselves as museums are seen as more favorable and worthy of visits, collaborations and support than other museums.

To ensure that inclusion of the word "museum" corresponds to the naming convention of the museum population, the names of the "Museums of the World" (MOW) database \parencite{deGruyter_2021_MOW}, a database containing over 55.000 museums, are analyzed.
In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial naming convention.

prevalence of museum founders to include the term museum in the name of their institution\footnote{While it would also be possible to construct inclusion in the MOW as an indicator of legitimacy, as it represents recognition of the organization as a museum by experts \parencite{Zuckerman_1999_illegitimacy}, preliminary investigations of the database indicated that it has been  updated only sparsely in recent years; thereby inclusion in it (or the lack therefore) does not constitute an accurate measurement of the extent of an institutions' recognition as a museum}.

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon May 27 11:25:41 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 294 & 0.584 & 0.604 & 0.49 & 0 & 1 \\ 
   & Gender - Female & 79 & 0.157 & 0.166 & 0.37 & 0 & 1 \\ 
   & Gender - Couple & 130 & 0.258 & 0.231 & 0.42 & 0 & 1 \\ 
   & Founder - alive &  &  & 0.903 & 0.30 & 0 & 1 \\ 
   & Founder - died recently &  &  & 0.019 & 0.13 & 0 & 1 \\ 
   & Founder - died 2+ years ago &  &  & 0.079 & 0.27 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 190 & 0.378 & 0.408 & 0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 104 & 0.207 & 0.189 & 0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 69 & 0.137 & 0.130 & 0.34 & 0 & 1 \\ 
   & Self-Identification - Other & 140 & 0.278 & 0.274 & 0.45 & 0 & 1 \\ 
   & Founder name in Museum name & 240 & 0.477 & 0.477 & 0.50 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  & 0.802 & 0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  & 0.144 & 0.35 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  & 0.053 & 0.23 & 0 & 1 \\ 
   & Exhibition any &  &  & 0.630 & 0.48 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  & 0.450 & 1.26 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  & 1.337 & 1.68 & 0.000087 & 10.81 \\ 
   & Nbr PM within 10km &  &  & 1.778 & 3.14 & 0 & 16 \\ 
   & Region - Africa & 8 & 0.016 & 0.012 & 0.11 & 0 & 1 \\ 
   & Region - Asia & 142 & 0.282 & 0.292 & 0.45 & 0 & 1 \\ 
   & Region - Europe & 248 & 0.493 & 0.497 & 0.50 & 0 & 1 \\ 
   & Region - Latin America & 23 & 0.046 & 0.042 & 0.20 & 0 & 1 \\ 
   & Region - North America & 72 & 0.143 & 0.138 & 0.34 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.020 & 0.019 & 0.13 & 0 & 1 \\ 
   & Time Period 2000-2004 &  &  & 0.101 & 0.30 & 0 & 1 \\ 
   & Time Period 2005-2009 &  &  & 0.166 & 0.37 & 0 & 1 \\ 
   & Time Period 2010-2014 &  &  & 0.258 & 0.44 & 0 & 1 \\ 
   & Time Period 2015-2019 &  &  & 0.331 & 0.47 & 0 & 1 \\ 
   & Time Period 2020-2024 &  &  & 0.145 & 0.35 & 0 & 1 \\ 
   & Great Recession (2008/09) &  &  & 0.076 & 0.27 & 0 & 1 \\ 
   & Covid Pandemic (2020/21) &  &  & 0.145 & 0.35 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

Overall the entire life span, the average hazard rate is 0.90\%, which allows comparison to other studies of NPO closure.
While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})

@@

Comparison to other forms of nonprofit organizations reported by \parencite{Gordon_etal_2013_insolvency}
places private museum at a risk similar to that of animal shelters and zoos (0.7\%), botanical \& environmental centers (0.8\%), colleges and universities (0.8\%), food and agricultural-oriented human service organizations (0.8\%) and  student and educational services (0.8\%).
While the diversity of non-profit organizations makes comparisons to its entirety difficult, it is still worthwhile to consider that the average hazard of private museums 0.90\% is around half that of that NPOs generally (1.58\%, see table \ref{tbl:litreview2} for studies on wider nonprofit populations).
It is furthermore substantially lower than that of youth centers (1.4\%), children-focused human services (2.4\%), K12 schools (1.8\%), mental health organizations (2.4\%) or performing arts organizations (3.7\%).
In fact, lower dissolution rates are only reported for historical societies (0.5\%) and libraries (0.2\%).

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon May 27 11:25:51 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pop4\_woenv}\\ 
 \hline
  \multicolumn{4}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .02 \; (0.34) & .10 \; (0.34) \\ 
   & Gender - Couple & -.10 \; (0.32) & -.15 \; (0.32) \\ 
   & Founder - died recently & 1.09 \; (0.61) & 1.03 \; (0.61) \\ 
   & Founder - died 2+ years ago & -.06 \; (0.55) & -.19 \; (0.56) \\ 
   \multicolumn{4}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .25 \; (0.42) & .44 \; (0.41) \\ 
   & Self-Identification - Collection & -.46 \; (0.54) & .00 \; (0.50) \\ 
   & Self-Identification - Other & 1.12 \; (0.31)^{***} & 1.04 \; (0.30)^{***} \\ 
   & AN Ranking - Included & .25 \; (0.35) & .26 \; (0.35) \\ 
   & AN Ranking - Dropped & .51 \; (0.50) & .52 \; (0.49) \\ 
   & Founder name in Museum name & .09 \; (0.28) & .06 \; (0.28) \\ 
   & Exhibition any & -.22 \; (0.27) & -.22 \; (0.27) \\ 
   \multicolumn{4}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .63 \; (0.35) &  \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) &  \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} &  \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} &  \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} &  \\ 
   & Great Recession (2008/09) & -1.61 \; (1.01) &  \\ 
   & Covid Pandemic (2020/21) & .39 \; (0.29) &  \\ 
   \hline
 & Museum-years & 6096 & 6096 \\ 
   & Closures & 68 & 68 \\ 
   & log. Likelihood & -338.36 & -351.64 \\ 
   & AIC & 712.73 & 725.28 \\ 
   & BIC & 752.68 & 749.69 \\ 
   \hline 
 \multicolumn{4}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

@@

\subsection*{Discussion}

Investigating the survival prospects of private museum furthermore illucidates the long-term development of the organizational form as a whole, as it provides insights into factors related to variation of sustainability and thereby into trends in composition.

Given the non-significant gender difference, it can be expected that (unless given a strong increase in founding by women) the population of private museums will continue to remain a man-dominated affair.
This finding also provides no evidence that female founders face gender-specific challenges that decrease the survival prospects of their private museums.

\subsubsection*{founder}

@@

For this study, I only investigated the occurence of closure events.
However, private museums can stop existing as private museums not just by closing down, but also by being transformed into other organizational forms.
One way in which this can happen is when other parties, such as local governments other philanthropists, foundations, or corporations become substantially involved in the ownership, governance and/or funding of the museum.
Sometimes this involves changes in the composition of the board of directors (or equivalent), with new parties gaining seats and hence influence in decision-making, thereby diminishing the private character of the museum to an extent that it no longer fits the working definition.
Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was not possible to generally determine the date of such transitions\footnote{As a consequence of this, they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing. However, as their numbers are limited to 25 entries in the database, the bias this introduces into closing risks is likely not substantial.}
The main issues that made the determination of the date impossible was the intransparency of these organizations (\texttt{event in the past, no track of organizational history}), as well as the gradual process.
As the presence of non-founder members does not categorically exclude a museum from being categorized as private museum as long as third-party influence is limited, this influence can grow until the museum bears little resemblance to its former self.
The possibility of other outcomes than surival and closures has been investigated for NPOs more generally
\parencite{Searing_2020_zombies,HernandezOrtiz_2022_discontinuity,Helmig_Ingerfurth_Pinz_2013_nonprofit}, and for private museums specifically: 
\textcite{Walker_2019_collector} argues that in the case of Germany, private museum founders turn to the state to ensure the survival of their projects in the form of public-private partnerships.
Investigating this process of transformation into a different organizational form thus provides fruitful avenue for further research.

environment can be measured more
\begin{itemize}
\item geocoding of other institutiosn
\item tax incentives
\item government spending
\end{itemize}
-> this might futher specify the niches in which PMs can endure

Museum characteristics might influence closing to a larger extent than has been considered here.
For example, museum size, facilities, as well as marketing and outreach activities might be related to long-term survival prospect.
For example, museums with more XXX might be more expensive to run, but on the other hand attract higher visitor numbers, cooperations and sponsorships. \texttt{liability of smallness}
Furthermore, having XXX might reflect founder commitment/resources.
While the original data collection included assessing various museum characteristics, such as XXX, it became clear that desk research was
Especially for closed museums data collection proved difficult, as in many cases websites had been shut down, and while in many cases snapshots of the main website were available in the Internet archive, \texttt{subdomains} were archived much less frequently, and sometimes inaccessible despite being archived due to changes in webtechnology (such as flash).
While it would be possible to
absence of evidence as evidence of absence

\textbf{supplementary material}

\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_pred_heatmap.pdf}
\caption{\label{fig:p_pred_heatmap}Predicted Avg. Hazard Rate on Regional PM Density and Population}
\end{figure}
\end{document}
